\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Galen}{Wang}{ \urlstyle{same}\href{https://github.com/galenhwang}{Github} |  \href{https://www.linkedin.com/in/galenwang}{LinkedIn} | \href{https://devpost.com/GalenWang}{Devpost}\\
604-441-4718 | \href{mailto:galenhwang@yahoo.ca}{galenhwang@yahoo.ca}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.3\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of British}
\subsection{Columbia}
\descript{BS, Combined Major in Business and Computer Science, Co-op}
\location{May 2020 | Vancouver, BC}
{\bf Honour: }Dean's Honour List, \\ Chancellor's Scholar \\
{\bf Cum. GPA: }3.9 / 4.33 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages:}
Javascript \textbullet{} Python \textbullet{} Java \textbullet{} C/C++ \\
Swift \textbullet{} SQL \textbullet{} Rails \\
\vspace{2mm}
\subsection{Frameworks /}
\subsection{Libraries:}
\vspace{1mm}
\location{Web}
React.js \textbullet{} AngularJS \textbullet{} Node.js \\
Express \textbullet{} jQuery \textbullet{} Socket.io \\
Electron \textbullet{} Bootstrap \\
\vspace{1mm}
\location{Python}
Django \textbullet{} NumPy \textbullet{} SciPy \textbullet{} Pandas \\
Scikit-learn \textbullet{} Matplotlib \textbullet{} TensorFlow \\
\vspace{2mm}
\subsection{Other:}
Git \textbullet{} MongoDB \textbullet{} PostgreSQL \textbullet{} AWS \\
Heroku \textbullet{} Google Cloud \textbullet{} Microsoft Azure \textbullet{}
R \textbullet{} \LaTeX\ \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Computer Hardware and OS \\
Computer Networking \\
Human-Computer Interaction \\
Intermediate Algorithm Design \\
\hspace{2mm}and Analysis \\
Internet Computing \\
Relational Databases \\
Software Engineering \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\begin{tabular}{ll}
2018 & 1\textsuperscript{st} Place – UBC Local Hack Day\\
2018 & Deloitte ThinkTech Finalist\\
2018 & Best Public Hack - HackDavis \\
2017 & TELUS Excellence in IT Award \\
2017 & 1\textsuperscript{st} Place – ProtoHack \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{EazyTeX}
\descript{| Full Stack Software Developer Intern }
\location{Dec 2018 – Present | Vancouver, BC}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Build a real-time interpreted WYSIWYG desktop application for LaTeX using React, Electron, Node, and Bootstrap
\item Improved loading and rendering by 5x by implementing performance fixes, including smart autosaving and endless scrolling
\item Building an Express server that integrates with PostgreSQL and AWS (S3 and Lightsail) for users to load and modify documents stored in the cloud.
\end{tightemize}
\sectionsep

\runsubsection{UBC}
\descript{| Undergraduate Teaching Assistant }
\location{Sep 2018 – Present | Vancouver, BC}
\begin{tightemize}
\item Developed course materials used for Differential Calculus (2018W1), and Logistics and Operations Management (2018W2)
\item Facilitate student learning during office hours and grade corresponding assignemnts, quizes, and exams
\end{tightemize}
\sectionsep

\runsubsection{Roblox}
\descript{| Product Manager Intern, Mobile Apps }
\location{Jan 2018 – Apr 2018 | San Francisco Bay Area, CA}
\begin{tightemize}
\item Met 83\% of 2018 Q1 product roadmap goals, shipping several features including swipe navigation, batch requests, and a new recommendation system
\item Improved app load time and crash rates, leading the mobile app to be ranked with a 4.5+ average rating and in the Top 10 Grossing Apps on Google Play
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Projects}
\href{https://devpost.com/software/emoci}{\runsubsection{EmoCI}}\\
\location{Dec 2018 | React.js, Python}
\textit{A web app that uses NLP and tone recognition to emotionally classify a movie scene.} \\ Each scene is rendered with emojis and a sentiment score reflecting the scene's mood. Built the backend with Python, leveraging third-party APIs along with use of a convolutional neural network.
\sectionsep

\href{https://devpost.com/software/growthdriver}{\runsubsection{GrowthDriver}}\\
\location{Mar 2018 – Apr 2018 | Python, Swift}
\textit{A game that calculates a player's preference for risk to construct a stock portfolio.} \\ Built the backend with Python with the NumPy and Pandas libraries for thw mean variance optimization algorithm, and IEX and BlackRock APIs for market data.
\sectionsep

\href{https://devpost.com/software/medvault}{\runsubsection{MedVault}}\\
\location{Mar 2018 | React.js, Rails}
\textit{A mobile app that allows first responders to  retrieve patient data during emergencies.} \\ Built the frontend with React Native with Redux for storing changes to a user's health history dynamically and dispatching information to our backend in Rails.
\sectionsep

\href{https://devpost.com/software/my6footprint}{\runsubsection{my6footprint}}\\
\location{Jan 2018 | Python, Swift, Rails, Google Cloud}
\textit{A mobile app that helps users track and optimize their carbon emissions.}\\ Built the frontend with Swift, creating visualizations of users' stats. Built the backend with Python, with Pandas, Scikit-learn, and Matploblib libraries used for the carbon allowance algorithm and linear regression model; Google Cloud (GCE and Storage).
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
